SunPy - Python for Solar Physics

### 2014-01-30 3-2-HEK.tex
bug fixes

SunPy accesses this information through the \texttt{hek} module, which was
developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 
use of the 
HEK API\footnote{For more information see 
\href{\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}}.
The current list of events maintained by the HEK and their properties can be 
found at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.

Simple HEK queries consist of start time, an end time, and an event type 
(Listing \ref{code:hek:simple}). Event types are specified as upper case, 
two letter strings, and are 
identical to the two letter abbreviations found at the HEK website, 
\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}

@@

HEK attributes differ from VSO attributes (Section \ref{ssec:vso}) in that many 
of them are wrappers that conveniently expose comparisons by overloading Python 
operators. This allows filtering of the HEK entries by the properties of the 
event. As was mentioned above, the HEK stores feature/event metadata obtained 
in different ways, known generally as feature recognition methods (FRMs). 
Example in Listing~\ref{code:hek:frm} filters the results of the previous 
result to return only those events that have the FRM 'SSW Latest Events'.  Multiple comparisons can be made by including more comma-separated
conditions on the attributes in the call to the HEK query method.
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType('FL'),
...                       hek.attrs.FRM.Name == 'SSW Latest Events')
>>> len(result)
9
\end{minted}
\caption{An HEK query that returns only those flares that were
  detected by the 'SSW Latest Events' feature recognition method.}
\label{code:hek:frm}
\end{listing}

Similar to the \texttt{vso} module, HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 
returns flares west of 50 arcseconds or those that have a peak flux above 
1000.0 (the units of the flux are FRM-dependent and are described at the HEK 
website).
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType('FL'),
...                       (hek.attrs.Event.Coord1 > 50) 
...                       or (hek.attrs.FL.PeakFlux > 1000.0))
\end{minted}
\caption{HEK query using the logical \texttt{or} operator.}
\label{code:hek:or}
\end{listing}
All FRMs report the required feature attributes (as described at 
\url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional attributes 
are FRM dependent.  If a FRM does not have one of the optional attributes, 
\texttt{None} is returned by the \texttt{hek} module.

>>>>

SunPy accesses this information through the \texttt{hek} module, which was
developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 
use of the 
HEK API\footnote{For more information see 
\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface}}.

Simple HEK queries consist of start time, an end time, and an event type 
(Listing~\ref{code:hek:simple}). Event types are specified as upper case, 
two letter strings, and are 
identical to the two letter abbreviations found at the HEK website,
%\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}
% schriste - above line causes an error, can't figure out why

@@

HEK attributes differ from VSO attributes (Section \ref{ssec:vso}) in that many 
of them are wrappers that conveniently expose comparisons by overloading Python 
operators. This allows filtering of the HEK entries by the properties of the 
event. As was mentioned above, the HEK stores feature/event metadata obtained 
in different ways, known generally as feature recognition methods (FRMs). 
Example in Listing~\ref{code:hek:frm} filters the results of the previous 
result to return only those events that have the FRM 'SSW Latest Events'.  Multiple comparisons can be made by including more comma-separated
conditions on the attributes in the call to the HEK query method.

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType('FL'),
...                       hek.attrs.FRM.Name == 'SSW Latest Events')
>>> len(result)
9
\end{minted}
\caption{An HEK query that returns only those flares that were
  detected by the 'SSW Latest Events' feature recognition method.}
\label{code:hek:frm}
\end{listing}

Similar to the \texttt{vso} module, HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 
returns flares west of 50 arcseconds or those that have a peak flux above 
1000.0 (the units of the flux are FRM-dependent and are described at the HEK 
website).
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType('FL'),
...                       (hek.attrs.Event.Coord1 > 50) 
...                       or (hek.attrs.FL.PeakFlux > 1000.0))
\end{minted}
\caption{HEK query using the logical \texttt{or} operator.}
\label{code:hek:or}
\end{listing}
All FRMs report the required feature attributes, but the optional attributes 
are FRM dependent.  If a FRM does not have one of the optional attributes, 
\texttt{None} is returned by the \texttt{hek} module.

### 2014-01-30 3-3-HELIO.tex
bug fixes

The HELiophysics Integrated Observatory (HELIO\footenote{For more information see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
compiled a list of web services which allows scientists to query and 
discover data throughout the heliosphere, from solar and magnetospheric data to planetary and 
inter-planetary data \citep{dps2012}.
HELIO is built with a Service-Oriented Architecture, 
i.e., its capabilities are divided into a number of tasks that are 
implemented as separate services. 
HELIO is made up of nine different public services, 
which allows scientists to search different catalogues of registered events, 
solar features, data from instruments in the heliosphere and other information 
such as planetary or spacecraft position in time. 
Additionally, HELIO provides a service that uses a 
propagation model to link the data in different points of the solar system by 
its original nature (e.g., Earth auroras are a signature of magnetic 
field disturbances produced few days before on the Sun).
In addition to the primary, web-based interface to 
HELIO, the services are available by API.

>>>>

The HELiophysics Integrated Observatory (HELIO\footnote{For more information see \url{http://helio-vo.eu}{http://helio-vo.eu}} has 
compiled a list of web services which allows scientists to query and 
discover data throughout the heliosphere, from solar and magnetospheric data to planetary and 
inter-planetary data \citep{dps2012}.
HELIO is built with a Service-Oriented Architecture, 
i.e., its capabilities are divided into a number of tasks that are 
implemented as separate services. 
HELIO is made up of nine different public services, 
which allows scientists to search different catalogues of registered events, 
solar features, data from instruments in the heliosphere and other information 
such as planetary or spacecraft position in time. 
Additionally, HELIO provides a service that uses a 
propagation model to link the data in different points of the solar system by 
its original nature (e.g., Earth auroras are a signature of magnetic 
field disturbances produced few days before on the Sun).
In addition to the primary, web-based interface to 
HELIO, the services are available by API.
